### 2019-12-17 asru_2019_maximizing_uniformity_of_distribution/poster/main.tex
Update the paper

\begin{minipage}[t]{1.0\linewidth}
\begin{center}
  \begin{minipage}[t]{0.1\textwidth}
    \centering
    \vspace{0pt}
    \includegraphics[width=10cm, valign=t]{samsung_research} % Logo or a photo of you, adjust its dimensions here
  \end{minipage} \hfill
  \begin{minipage}[t]{0.7\textwidth}
    \begin{center}
  \huge \color{NavyBlue} 
      \textbf{Power-law nonlinearity with maximally uniform distribution criterion for
      improved neural network training in automatic speech recognition} \\
      \LARGE \textbf{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda}
  \\
\LARGE Samsung Research, Seoul, South Korea\\ % University/organization
\large \{chanw.com, mk0211.shin, ky85.kim, d.gowda\}@samsung.com
    \end{center}
  \end{minipage}
  \begin{minipage}[t]{0.1\textwidth}
    \begin{center}
    \includegraphics[width=10cm]{samsung_research} % Logo or a photo of you, adjust its dimensions here
    \end{center}
  \end{minipage} \hfill
\end{center}
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Department Name\\ % Address
%University Name\\
%123 Broadway, State, Country\\\\
%Phone: +1 (000) 111 1111\\ % Phone number
%Email: \texttt{john@LaTeXTemplates.com}\\ % Email address
%\end{minipage}
%

@@

\section{Motivation}

\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database \cite{n_jaitly_icml_workshop_2013_00}.
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length for the frequency warping from
          the one used in feature processing for performance optimization.
    \end{itemize}
\end{enumerate}

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
  \section{Maximization of Distribution Uniformity}

\begin{Figure}
  \begin{center}
    {
      \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
      \label{fig:mel_filterbank_energy_histogram}
    }   
    \\  
    {
      \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
      \label{fig:power_function_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \\  
    {
      \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
      \label{fig:histogram_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \captionof{figure} {
      The Probability Density Functions for the third filterbank channel
       of (a): the mel filterbank energy $p[m, l], l = 3$ in  
       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD 
      output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
      the histogram based-MUD in \eqref{eq:histogram_mud}. 
      \label{fig:pdf_mud}
    }   
   \vspace{-7mm}
  \end{center}
\end{Figure}

%\begin{center}
%  \includegraphics[width=0.2\linewidth]{power_function_based_mud_output_histogram}

@@

\section{End-to-End Speech recognition}

\begin{minipage}{1.0\linewidth}
  {
    \normalsize
  \begin{center}
  \resizebox{180mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
  \end{center}
\captionof{figure}{ 
  The structure of the entire end-to-end speech recognition system.}
  }
\end{minipage}

  We used the RETURNN speech recognition system
  \cite{a_zeyer_interspeech_2018_00} with various modifications:
    \begin{itemize}
      \item{Gradient clipping and learning-late warm-up.}
      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$) in PNCC \cite{C_Kim_IEEETran_2016_1}.
      \item{Modified shallow fusion with a Transformer LM}

        \begin{align}
  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
  |\vec{x}[0:M], y_{0:l} \right)
  \nonumber \\
                           & \qquad - \lambda_p \log P(y_l)
                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
                           \label{eq:lm_fusion}
\end{align}

    \end{itemize}

@@

\section{Experimental Results}
\begin{itemize}
  \item For training, we used { \bf the Librispeech train-clean and
    train-other}.
  \item For evaluation, we used { \bf the test-clean and test-other of this Libri
    Speech database. }
\end{itemize}

@@

            \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
                & test-other  &  13.97  \% & 13.56 \%
                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
                & average     &   9.02  \% &  8.75 \%
                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
        \hline
     \end{tabular}
     \vspace{-4mm}
\end{minipage}
 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

@@

%
\color{SaddleBrown} % SaddleBrown color for the introduction
\section{Conclusions}
%
{ \color{red}
We achieved 2.44 \% WER and 8.29 \% WER
  on the Librispeech {\it test-clean} and {\it test-other} databases.
To the best of our knowledge, the 2.44 \% WER on the {\it test-clean}
is the best result ever reported on this database
}
%
%
\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database. \cite{n_jaitly_icml_workshop_2013_00}
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length (50 {\it ms}) for the frequency warping from
          the one used in feature processing (25 {\it ms}).
    \end{itemize}
  \item Applies the power-mel feature.
  \item Applies a modified shallow-fusion with a Transformer LM.
\end{enumerate}
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
%----------------------------------------------------------------------------------------
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
\end{multicols}
\end{document}

>>>>

\begin{minipage}[t]{1.0\linewidth}
\begin{center}
  \begin{minipage}[t]{0.1\textwidth}
    \centering
    \vspace{0pt}
    \includegraphics[width=10cm, valign=t]{samsung_research} % Logo or a photo of you, adjust its dimensions here
  \end{minipage} \hfill
  \begin{minipage}[t]{0.7\textwidth}
    \begin{center}
  \huge \color{NavyBlue} 
      \textbf{Power-law nonlinearity with maximally uniform distribution criterion for
      improved neural network training in automatic speech recognition} \\
      \LARGE \textbf{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda}
  \\
\LARGE Samsung Research, Seoul, South Korea\\ % University/organization
\large \{chanw.com, mehul3.kumar, ky85.kim, d.gowda\}@samsung.com
    \end{center}
  \end{minipage}
  \begin{minipage}[t]{0.1\textwidth}
    \begin{center}
    \includegraphics[width=10cm]{samsung_research} % Logo or a photo of you, adjust its dimensions here
    \end{center}
  \end{minipage} \hfill
\end{center}
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Department Name\\ % Address
%University Name\\
%123 Broadway, State, Country\\\\
%Phone: +1 (000) 111 1111\\ % Phone number
%Email: \texttt{john@LaTeXTemplates.com}\\ % Email address
%\end{minipage}
%

@@

\section{Summary about Maximum Uniformity of Distribution (MUD)}
%
\begin{itemize}
  \item We developed a novel approach for obtaining {the \color{Navy} nonlinearity function} in a {\it data-driven } way.
  \item This approach is based on the assumption that neural-network training would be easier 
  and the converged parameters would show better
  performance when feature distribution is not too much
  skewed or too much concentrated in an extremely narrow interval.

  \item The criterion is to maximize {\color{Navy} the Uniformity of Distribution}.
  \item We develop two different types of MUD. 
    \begin{itemize}
      \item Power Function-Based MUD
      \item Histogram-Based MUD
    \end{itemize}
  \item Power function-based MUD shows better results than the histogram-based MUD.
  \item We achieved 4.02 \%  WER on test-clean and 13.34 \% WER on test-other without using any Language Models (LMs).
  \item This approach may be extended to other domains as well.
\end{itemize}
%
%
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
  \section{Maximization of Distribution Uniformity}

\begin{itemize}
  \item The MUD nonlinearity is applied to mel-filterbank energy for each channel.
\end{itemize}

\subsection{Power-function based maximization of distribution
uniformity}
%
\begin{itemize}
\item The transformation based on the power function:
\begin{align}
  \mathbf{Y} = \sigma_{p} \left(\mathbf{X} \right) = (X - x_{\text{min}})^{\alpha}.
    \label{eq:power_mud}
\end{align}
%
\item We expect $Y$ to follow the following uniform distribution:
\begin{align}
 \mathbf{Y} \sim 
  \mathcal{U}(0, \left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha} ).
    \label{eq:pdf_y}
\end{align}
%
\item
The log likelihood of the data $X$ assuming the PDF in \eqref{eq:pdf_y}
is given by (Refer to the paper for mathematical details):
%
%
\begin{align}
  \mathcal{L}\left(\alpha ; X\right) 
      & = \sum_{i=0}^{N-1} \ln p_{\mathbf{X}} \left( x_i \right)  \nonumber \\
      & = \sum_{i=0}^{N-1} 
              \ln \left[ \frac{ \alpha (x_i - x_{\text{min}} )^{\alpha-1}}  
              {\left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha}} \right]  \nonumber \\
      & = N \ln(\alpha) + \left(\alpha-1 \right) \sum_{i=0}^{N-1}
        \ln \left(x_i - x_{\text{min}} \right)  
       - N \alpha \ln \left(x_{\text{max}} - x_{\text{min}} \right).
        \label{eq:x_likelihood}
\end{align}
%
%
%
%
%
\item 
%
The following $\hat{\alpha}$ maximizes the log-likelihood of $\mathcal{L}\left(\alpha ; X\right)$
(Refer to the paper for mathematical details).
%
%
\begin{align}
  \hat{\alpha} = \frac{1}{
    \ln \left(\max \left\{x_i - x_{\text{min}}, \delta \right\} \right)
    - \frac{1}{N} \sum_{i=0}^{N-1} \ln \left(x_i - x_{\text{min}}\right)}.
  \label{eq:alpha_estimation}
\end{align}
%
%
\end{itemize}
%
%
  \begin{Figure}
    \begin{center}
      \includegraphics[width=170mm]{estimated_power_coeff}
      \captionof{figure} {
        \label{fig:estimated_power_coeff}
        The estimated power coefficients for each mel filterbank channels using
        \eqref{eq:alpha_estimation}.
      }
    \end{center}
    \vspace{-7mm}
  \end{Figure}
%
%
%
\subsection{Histogram-based maximization of distribution uniformity}
\begin{itemize}
\item The distribution is uniformized using the empirical CDF (Refer to the paper for mathematical details):
\begin{align}
  \mathbf{Y} = \sigma_{np}(\mathbf{X}) 
     = F_u^{-1} \left(\hat{F}_x(\mathbf{X})\right)
      = \hat{F}_x(\mathbf{X}).
  \label{eq:histogram_mud_simple}
\end{align}
\end{itemize}
%
%
\begin{minipage}[]{0.54\linewidth}
  \begin{Figure}
  \begin{center}
    {
      \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
      \label{fig:mel_filterbank_energy_histogram} \\
      (a)
    }   
    \\  
    {
      \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
      \label{fig:power_function_based_mud_output_histogram} \\
      (b)
    }   
    \\  
    {
      \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
      \label{fig:histogram_based_mud_output_histogram} \\
      (c)
    }   
    \\
    \captionof{figure} {
      The Probability Density Functions for the third filterbank channel
       of (a): the mel filterbank energy $p[m, l], l = 3$ 
       , (b): the power-function based MUD 
      output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
      the histogram based-MUD in \eqref{eq:histogram_mud_simple}. 
      \label{fig:pdf_mud}
    }   
   \vspace{-7mm}
  \end{center}
\end{Figure}
\end{minipage}
%
%
\begin{minipage}[]{0.45\linewidth}
  \begin{Figure}
  \begin{center}
  \resizebox{150mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
  \end{center}
  \captionof{figure}{ 
  The structure of the entire end-to-end speech recognition system.}
  \end{Figure}
\end{minipage}

%
%\begin{center}
%  \includegraphics[width=0.2\linewidth]{power_function_based_mud_output_histogram}

@@

\section{End-to-End Speech recognition}
 We used the RETURNN speech recognition system \cite{a_zeyer_interspeech_2018_00} with various modifications:
    \begin{itemize}
      \item{MoCha\cite{k_kim_asru_2019_00} and the modified beam search decoder.}
      \item{Gradient clipping, modified learning-late warm-up, and so on.}
    \end{itemize}

@@

\section{Experimental Results}

\begin{itemize}
\item \textbf{LibriSpeech experiments} (960-hr training and evaluation on LibriSpeech {\tt test-clean} and {\tt test-other} ) 
\end{itemize}

@@

            \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
                & test-other  &  13.97  \% & 13.56 \%
                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
                & average     &   9.02  \% &  8.75 \%
                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
        \hline
     \end{tabular}
     \vspace{-4mm}
\end{minipage}
\begin{itemize}
\item The Power-Function Based MUD shows slightly better result than the power-law nonlinearity with the power coefficient of $\frac{1}{15}$ \cite{
C_Kim_IEEETran_2016_1}.
\item We hypothesize that the reason why histogram-based MUD does slightly worse than the power-
function based MUD is that it somewhat obscured the energy boundary between speech vs non-speech.
\end{itemize}
 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

@@

%

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
%----------------------------------------------------------------------------------------
\small
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
\end{multicols}
\end{document}
